### 2020-04-25 final_report/methodology.tex
more detailed figure 9 and 10

Aiming to provide objective comparison of a diverse set of surrogate model
classes, we define a multitude of metrics to be tracked during experiments.
Following the motivation of this work, two desirable properties of surrogates
arise: (i) their capability to approximate the TBR MC model well and (ii) their time of evaluation. An ideal surrogate would maximise
the former while minimising the latter.

\Cref{tbl:metrics} provides exhaustive listing and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for model comparison between works as
they maintain invariance with respect to the selected domain and image space.
For analysis of evaluation time, surrogates are assessed in terms of wall time
elapsed during training and predicition. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single sample. Even though some surrogates support acceleration
by means of parallelisation, measures were taken to ensure sequential
processing of samples to achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks, which are
notoriously slow to train on conventional CPU architectures in serialised
setting.}

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llrl}
		\toprule
		Regression performance metrics	& Mathematical formulation / description &
		\multicolumn{2}{c}{Ideal value [units]} \\
		\midrule
		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
									& [TBR] \\
		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
		\midrule
		Evaluation time metrics	& {} & {} & {} \\
		\midrule
		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
		$\hat{f}(x)$})/N$	& 0 & [ms] \\
		Relative speedup $\sigma$	& $(\text{wall evaluation time of $f(x)$}) /
		(N\overline{t}_{\text{pred.}})$	&
		$\to\infty$ & [rel.] \\
		\bottomrule
		\end{tabular}
	}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

>>>>

Aiming to provide objective comparison of a diverse set of surrogate model
classes, we define a multitude of metrics to be tracked during experiments.
Following the motivation of this work, two desirable properties of surrogates
arise: (i) their capability to approximate the TBR MC model well and (ii) their
complexity. An ideal surrogate would maximise
the former while minimising the latter.

\Cref{tbl:metrics} provides exhaustive listing and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for model comparison between works as
they maintain invariance with respect to the selected domain and image space.
For complexity analysis, surrogates are assessed in terms of wall time
elapsed during training and predicition. This is motivated by common practical use
cases of our work, where models are trained and used as drop-in replacements for the
expensive MC TBR model. Since training set sizes remain to be determined, all times are
reported per a single sample. Even though some surrogates support acceleration
by means of parallelisation, measures were taken to ensure sequential
processing of samples to achieve comparability between considered
models.\footnote{The only exception to this are artificial neural networks, which are
notoriously slow to train on conventional CPU architectures in serialised
setting.}

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llrl}
		\toprule
		Regression performance metrics	& Mathematical formulation / description &
		\multicolumn{2}{c}{Ideal value [units]} \\
		\midrule
		Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
									& [TBR] \\
		Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left\{ |y^{(i)} -
		\hat{y}^{(i)}| \right\} $	 & 0 & [TBR] \\
		Coefficient of determination $R^2$	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
		\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 & [rel.] \\
		Adjusted $R^2$	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 & [rel.] \\
		\midrule
		Complexity metrics	& {} & {} & {} \\
		\midrule
		Mean training time $\overline{t}_{\text{trn.}}$	& $(\text{wall training time of
		$\hat{f}(x)$})/N_0$ 	& 0 & [ms] \\
		Mean prediction time $\overline{t}_{\text{pred.}}$	& $(\text{wall prediction time of
		$\hat{f}(x)$})/N$	& 0 & [ms] \\
		Relative speedup $\sigma$	& $(\text{wall evaluation time of $f(x)$}) /
		(N\overline{t}_{\text{pred.}})$	&
		$\to\infty$ & [rel.] \\
		\bottomrule
		\end{tabular}
	}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

### 2020-04-25 final_report/results.tex
Repaired images and conclusion formatting.
more detailed figure 9 and 10

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 0-3}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 100-103}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 200-203}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered class, plotted in
	terms of mean prediction time and regression performance (as~$R^2$) on
	selected slices of run~2, evaluated in experiment~1.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	% TODO: only a placeholder, regenerate when data becomes available
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
	\vspace{-4ex}
\end{wrapfigure}

@@

@@

\begin{wrapfigure}{r}{0.4\textwidth}
  \vspace{-60pt}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
    \label{fig:sintoy}
  \end{center}
  \vspace{-30pt}
\end{wrapfigure}

>>>>

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 0-3}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 100-103}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		% TODO: only a placeholder, regenerate when data becomes available
		\caption{Run 2, batches 200-203}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered class, plotted in
		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) on selected slices of run~2, evaluated in experiment~1.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

% TODO: add table here or in appendix with hard numbers, for each class take 20
% best performing models from each slice, concatenate and calculate mean and std
% for each metric

% TODO: do the same thing for the second experiment
\newpage
\begin{wrapfigure}{r}{0.333\textwidth}
	\centering
	\vspace{-3ex}
	\includegraphics[width=\linewidth]{exp2_time_vs_reg}
	% TODO: only a placeholder, regenerate when data becomes available
	\caption{Results of experiment~2, plotted analogously
	to~\cref{fig:exp1-time-vs-reg}.}
	\label{fig:exp2-time-vs-reg}
	\vspace{-4ex}
\end{wrapfigure}

@@

% TODO: add tables here or in appendix with scaling results; for each metric
% create a table with rows = classes, columns = training set size, cells = mean +/- std
% it may be a lot, decide on placement and layout!

@@

\newpage

\begin{wrapfigure}{r}{0.4\textwidth}
  \vspace{-60pt}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
    \label{fig:sintoy}
  \end{center}
  \vspace{-10pt}
\end{wrapfigure}
